### 2015-11-06 CVPR16/Source/experiments2.tex
changes

\subsection{Localization Experiments}
We report errors in translation error and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}. We compare four combinations of energies.  The energy $\EnergyTrackNoOcc$ represents the point tracks energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $\Ptransmission$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the modification of $\Lambda_k$ that accounts for occlusion. The results show that the use of continuous occlusion model improves the localization accuracy in terms of the translation error, which is he most significant metric affected by all cues. Occlusion modeling for detection improves localization, but penalizes dimension since we explicitly allow greater uncertainty in occluded edges of the bounding box.

>>>>

\subsection{Localization Experiments}
We report errors in translation error and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}. We compare four combinations of energies.  The energy $\EnergyTrackNoOcc$ represents the point tracks energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $\Ptransmission$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the modification of $\Lambda_k$ that accounts for occlusion. The results show that the use of continuous occlusion model improves the localization accuracy in terms of the translation error, which is he most significant metric affected by all cues. Occlusion modeling for point tracks is always beneficial, while that for detection improves localization, but penalizes dimension since we explicitly allow greater uncertainty in occluded edges of the bounding box. Note that none of our energies optimize yaw angles for static objects, which can be handled in practice through either the detector orientation or external information such as lane geometry.
